%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template adapted for Aşkın Kadir Çekim
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style 

\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Aşkın Kadir Çekim} % Your name 
\address{Karlsruhe, Germany \\ LinkedIn: linkedin.com/in/askinkadir/} % Your address 
\address{+49 162 760 9755 \\ kadircekim.07@gmail.com} % Your phone number and email

\begin{document}  

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf B.Sc. Computer Science} \hfill {2025 -- Present} \\
Karlsruhe Institute of Technology (KIT), Karlsruhe, Germany \\[0.1cm]
{\bf B.Sc. Computer Engineering (Transferred)} \hfill {2023 -- 2024} \\
Marmara University, Istanbul, Turkey \\[0.1cm]
{\bf Private Antalya Final Science High School} \hfill {2022 -- 2023} \\
Antalya, Turkey \\[0.1cm]
{\bf Dr. İlhami Tankut Anatolian High School} \hfill {2019 -- 2022} \\
Antalya, Turkey

\end{rSection} 

%----------------------------------------------------------------------------------------
% PROFILE / SUMMARY
%----------------------------------------------------------------------------------------

\begin{rSection}{Profile}

Computer Science student with a strong foundation in software development, coding since the age of 10. Passionate about building products at the intersection of artificial intelligence, blockchain, and emerging technologies. Experienced in hackathons, mobile and web development, and integrating AI tools into real-world workflows.

\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{OmmaWorks}{March 2024 -- Present}{Business Operations Specialist}{Remote}
\item Researched, evaluated, and integrated AI tools (ChatGPT, Gemini, and other LLM-based solutions) to improve efficiency across departments.
\item Automated internal workflows by embedding AI-driven solutions into daily operations, increasing team productivity.
\item Structured and optimized the company Knowledge Base using AI-assisted documentation and search capabilities.
\item Developed and maintained BI dashboards (initially with Retool, later with Metabase) incorporating AI-enhanced analytics for data-driven decision-making.
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  

Programming Languages & JavaScript, Python, Java, Dart, C, C++, SQL \\[0.1cm]

Frameworks \& Libraries & Flutter, React.js, Next.js, Vue.js, Express.js, JavaFX, FastAPI \\[0.1cm]

Databases \& Cloud & MySQL, MS SQL, MongoDB, Firebase \\[0.1cm]

Tools \& OS & Debian, Ubuntu, Notion, Metabase, Retool, Google Workspace, Microsoft Office \\

\end{tabular}   

\end{rSection}

%-------------------------------------------------------------------------------
% PROJECTS / HACKATHONS
%-------------------------------------------------------------------------------

\begin{rSection}{Projects and Hackathons}

\begin{rSubsection}{Proactive EV Co-Pilot}{2025}{Winner -- Mercedes-Benz Tech Innovation Hackathon}{Navigation: The Nexus 2025}
\item AI-powered EV itinerary planning assistant for multi-stop routing.
\item Implemented user preference learning, constraint-aware scoring, and real-time charging insights.
\item Built a full architectural prototype with a Flutter frontend, HERE APIs, a preference-based ranking engine, and an LLM-driven intent parser.
\item Awarded as a winner for innovation in intelligent EV navigation. 
\item Link: https://www.linkedin.com/feed/update/urn:li:activity:7400505797337747456/
\end{rSubsection}

\begin{rSubsection}{Twinify -- Your AI-Powered Digital Twin for WhatsApp}{2025}{Winner -- Nosu AI Hackathon}{Exploratory use of LLMs and Vision Models}
\item Built an AI-powered digital twin that mirrors my personality, voice, and communication style on WhatsApp.
\item Integrated OpenAI GPT for conversational intelligence, ElevenLabs for realistic voice cloning, and WhatsApp Web.js for messaging.
\item Implemented a SQLite-backed memory layer to preserve long-term context and enable rich, ongoing conversations.
\item Recognized as a winner in the "Exploratory use of LLMs and Vision models" track at the Nosu AI Hackathon.
\item Link: https://devpost.com/software/twinify-your-ai-powered-digital-twin-for-whatsapp
\end{rSubsection}

\begin{rSubsection}{UNITE -- Government Procurement Platform}{2020}{4th Place -- \#EuVsVirus Hackathon}{Crisis-Time Platform}
\item Designed a crisis-time platform to streamline public procurement, acting as an ``Alibaba for government tenders''.
\item Developed using Node.js to enable efficient tender discovery and matching between governments and suppliers.
\item Achieved 4th place in the \#EuVsVirus Hackathon at the age of 14.
\item Link: https://devpost.com/software/unite-government-procurement-platform
\end{rSubsection}

\begin{rSubsection}{Liberta -- Decentralized Social Media}{--}{Blockchain-Based Social Platform}{Privacy and Ownership}
\item Designed a blockchain-based social media platform focusing on privacy, data ownership, and censorship resistance.
\item Implemented the frontend using Vue.js and leveraged the NEO N3 blockchain for back-end operations.
\item Provided a decentralized alternative to traditional social media platforms.
\item Link: https://devpost.com/software/liberta-the-social-media-that-managed-by-users
\end{rSubsection}

\begin{rSubsection}{DON8 -- Donation Made Great}{--}{Non-Profit Donation Platform}{Flutter Mobile App}
\item Built a cross-platform mobile app using Flutter to encourage charitable giving through everyday purchases.
\item Focused on use cases in the food and drink sector to integrate donations seamlessly into daily life.
\item Link: https://devpost.com/software/don8-donation-made-great
\end{rSubsection}

\end{rSection} 

%--------------------------------------------------------------------------------------
%   LANGUAGES
%--------------------------------------------------------------------------------------

\begin{rSection}{Languages}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }  
Turkish & Native \\ 
English & Advanced\\
German & Advanced\\
\end{tabular}

\end{rSection}

%--------------------------------------------------------------------------------------
%   ADDITIONAL INFORMATION
%--------------------------------------------------------------------------------------

\begin{rSection}{Additional Information}

\begin{itemize}
\item Driving License: Class B.
\item Strong interest in AI, EV mobility, developer tooling, and large language model applications.
\item Comfortable working in cross-functional, international teams and hackathon-style fast-paced environments.
\end{itemize}

\end{rSection}

\end{document}